\documentclass{article}

\usepackage{url}

% variables
\newcommand{\blockWidth}{w}
\newcommand{\blockLength}{l}
\newcommand{\blockHeight}{h}
\newcommand{\blockDataSize}{sz}
\newcommand{\targetFPS}{60 fps }
\newcommand{\playerLoadDistance}{$P_{loadDist}$}

\begin{document}
\title{Requirements for MyCraft}
\author{Christopher Gammage}
\maketitle

\begin{abstract}
MyCraft is highly customizable sandbox multiplayer block building game engine.  It uses a built in scripting engine to allow developers to create plugins that build the game. 
Every aspect of the engine should be swappable with Plugin Components.  Every plugin should
have a high degree of configurability.   
\end{abstract}

\tableofcontents

\section{Strategy and Overview}
\subsection{Goals and Objectives}
The goal of this game engine is to create an open source block based engine that others
can make games out of.  Any person who knows C++ and reads the development guide, should
be able to create a plugin and modify they game however they see fit.  It should allow
multiplayer and have a means for syncing plugin configurations.
\subsection{Strategic Roadmap}
The first beta of the game should have the overall structure of the plugin framework
and have a few default plugins already existing.  It should have a rudimentary 
world generation module and allow people to play around in the sandbox.  When
the system is stable enough that a plugin developer can make a full game out of it, it
will be released as version 1.0.  The game will grow through a plugin developer 
community and their their interactions with the players.
\subsection{Customer Categories}
There are two customer targets.  The first are the players of the game and the second
are the plugin developers.  Plugin developers are also players.  The age range of players
could be anywhere between 6 and 65.  The game should not contain anything offensive for
any customer in that range.
\subsection{Competitive Strengths and Weaknesses}
One advantage of this game / engine over other similar games will be that it is 
out of the box completely customizeable.  There will be a strong plugin API that will
make plugin development easy.  It will be OS-independent and because of it's native
C++ code, it should have great performance.  Since it will be open source and community driven, there will be more flexability in how the game engine develops. 
\section{Bill of Materials}

\subsection{The Game Client}
\subsection{The Game Server}
\subsection{Development SDK}
The SDK will make it easy for plugin developers to start working on plugins for the game.
\subsection{Development Guide}
A guide for making plugins is very important.  Plugin developers are what will make the
game successful and they should be able to easily learn the SDK.  It should include the
fully documented plugin API as well as several tutorials on how to use common features.
\section{Internally Committed Requirements}

\section{Externally Committed Requirements}

\section{Highly Desirable Requirements}

\section{Future Requirements}

\section{Features Not Being Implemented}

\end{document}